Notes on area-length problem for CLE

### 2014-04-01 area-length/notes.tex
Harmonic measure and SLE Hausdorff dimension is written

Consider a closed curve. Harmonic measure of some part of the curve can be understood as a charge of
that part if the curve is made of conducting material and its total charge is equal to one. 
Closed curve can be covered by small circles of radius $r$ centered at points
$z_{i}$. Consider one such circle. The curve divides the circle into two parts, inner and outer
w.r.t. to curve. Outer part can be conformally mapped to the unit disk. Denote this map by $w(z)$.
With the normalization such that one point is fixed and derivative at infinity is equal to one the
moments of harmonic measure in small circle of radius $r$ scale as
\begin{equation}
  \label{eq:116}
  \mu(r)\sim |w(r)|\sim r |w'(r)|
\end{equation}
So scaling of the moments of $\mu(r)$ are determined by scaling of $|w'(r)|$:
\begin{equation}
  \label{eq:117}
  \prec |w'(r)|^{h}\succ \sim r^{\Delta(h)}, \quad r\to 0
\end{equation}

@@

Following relations hold for multifractal spectrum and anomalous exponents:
$\tilde\tau(h)=\tau(h)-\tau(0)$, $\Delta_{bulk}(h)=\delta(h)-\delta(0)$, $d_{H}=1+\Delta_{bulk}(1)$

@@

@@

Pinning operator creates one curve passing through the point in the bulk, so it is $\psi_{0,1}$. Its
conformal weight is
\begin{equation}
  \label{eq:148}
  h_{0,1}=\frac{8-\kappa}{16},
\end{equation}
and Hausdorff dimension is
\begin{equation}
  \label{eq:149}
  d_{H}=2-2h_{0,1}
\end{equation}

To see it one can consider circle of small radius $\varepsilon$ centered at $z$. Put some conformal
boundary condition on one half of the circle and another condition on the rest of the circle. Then
critical curve would join the points of change in boundary conditions. The expectation values of
observables in this geometry are given by CFT correlation functions with two boundary condition
changing operators inserted:
\begin{equation}
  \label{eq:119}
  \left< \Psi_{12}(z')\Psi_{12}(z'')\right>
\end{equation}
where $|z'-z|\leq \varepsilon$ and $|z''-z|\leq \varepsilon$. The boundary condition changing
operators in Coulomb gas picture can be presented as the vertex operators
$V_{\alpha_{12}}=e^{i\sqrt{2}\alpha_{12}\varphi(z)}$. When $\varepsilon\to 0$ we can fuse this two
operators to single operator $V_{2\alpha_{12}}$. Note that $\alpha_{12}=-\frac{1}{2}\alpha_{-}$
\eqref{eq:55}, so $V_{2\alpha_{12}}\sim V_{-\alpha_{-}}\sim V_{\alpha_{+}}$ (?)

The moments of harmonic measure are connected with the CFT correlation functions by
\begin{equation}
  \label{eq:118}
  \left<O_{h}(r) \Psi_{10}(0)\Psi(\infty)\right>\sim r^{h'-2h}\prec |w'(r)|^{h}\succ
\end{equation}

>>>>

Consider a closed curve. Harmonic measure of some part of the curve can be understood as a charge of
that part if the curve is made of conducting material and its total charge is equal to one. 
Closed curve can be covered by small circles of radius $r$ centered at points
$z_{i}$. Consider one such circle. The curve divides the circle into two parts, inner and outer
w.r.t. to curve. Outer part can be conformally mapped to the unit disk. Denote this map by $w(z)$.
With the normalization such that one point is fixed and derivative at infinity is equal to one the
moments of harmonic measure in small circle of radius $r$ scale as
\begin{equation}
  \label{eq:116}
  \mu(r)\sim |w(r)|\sim r |w'(r)|
\end{equation}
This scaling follows from electrostatic interpretation of harmonic measure, since $\mu(r)$ is charge
inside the circle and by Gauss theorem it is equal to the flux of electric field through the
boundary. Typical absolute value of electric field on the circle is $|w'(r)|$ and boundary length is
$2\pi r$.

So scaling of the moments of $\mu(r)$ is determined by scaling of $|w'(r)|$:
\begin{equation}
  \label{eq:117}
  \prec |w'(r)|^{h}\succ \sim r^{\Delta(h)}, \quad r\to 0
\end{equation}

@@

Following relations hold for multifractal spectrum and anomalous exponents:
$\tilde\tau(h)=\tau(h)-\tau(0)$, $\Delta_{bulk}(h)=\delta(h)-\delta(0)$. The most important for us
here is the connection of Hausdorff dimension and local anomalous exponent 
\begin{equation}
  \label{eq:150}
  d_{H}=1+\Delta_{bulk}(1)
\end{equation}

@@

Correlation functions in Coulomb gas picture are easily calculated:
\begin{equation}
  \label{eq:157}
  \left< V_{\alpha_{1}}(z_{1})\dots
    V_{\alpha_{n}}(z_{n})\right>=\prod_{i<j}(z_{i}-z_{j})^{2\alpha_{i}\alpha_{j}}, \quad \mbox{if}\quad \sum_{i}\alpha_{i}=2\alpha_{0}
\end{equation}

@@

Pinning operator creates one curve passing through the point in the bulk, so it is $\psi_{0,1}$. Its
conformal weight is
\begin{equation}
  \label{eq:148}
  h_{0,1}=\frac{8-\kappa}{16},
\end{equation}
We want to show that Hausdorff dimension is
\begin{equation}
  \label{eq:149}
  d_{H}=2-2h_{0,1}
\end{equation}

To do so we need to connect local anomalous scaling exponents with conformal weights of vertex
operators. Local moments of harmonic measure $\mu(z,r)^{h}$ are connected with conformal maps.
Consider conformal map $w$ of the exterior of critical curve $\gamma$ to upper half-plane or unit
circle. Normalize this map such that $w(z)=z$ and $w(z'\to\infty)=z'+o(z')$. As we have seen the
scaling of $w$ near $z$ is related to harmonic measure.

The partition function $Z(0,L)$ of configurations that contain a closed curve passing through the
points $0$ and $L$ is given by the correlator of two pinning operators $\psi_{0,1}$:
\begin{equation}
  \label{eq:151}
  \frac{Z(0,L)}{Z}=\left<\psi_{0,1}(0)\psi_{0,1}(L)\right>,
\end{equation}
where $Z$ is partition function of all configurations.

The partition function $Z(0,L)$ can be calculated as the product of partition functions inside and
outside of the curve averaged over all possible curves:
\begin{equation}
  \label{eq:152}
  Z(0,L)=\prec Z_{\gamma}^{\mathrm{int}} Z_{\gamma}^{\mathrm{ext}}\succ
\end{equation}
To get the moments of harmonic measure we need to insert some operator $\mathcal{O}(r)$ (product of
operators), for charge neutrality we need to add another one at infinity $\mathcal{O}(\infty)$.
Since we are interested in small $r<<L$ we can fuse $\mathcal{O}(\infty)$ with $\psi_{0,1}(L)$ into
$\Psi(\infty)$. So we need to compute correlation function $\left<\psi_{0,1}(0) \mathcal{O}(r)
  \Psi(\infty)\right>$. It can be done in two ways, directly and averaging
$\left<\mathcal{O}(r)\mathcal{O}(\infty)\right>_{\gamma}$ over all curves:
\begin{equation}
  \label{eq:153}
  \left<\psi_{0,1}(0) \mathcal{O}(r)\Psi(\infty)\right>= \prec
  \left<\mathcal{O}(r)\mathcal{O}(\infty)\right>_{\gamma}^{\mathrm{ext}} Z_{\gamma}^{\mathrm{ext}} Z_{\gamma}^{\mathrm{int}}\succ
\end{equation}
The correlation function of operators $\mathcal{O}$ is statistically independent from other factors
and has all the dependence on $r$. Apply to this correlation function conformal map $w$:
\begin{equation}
  \label{eq:154}
  \left<\mathcal{O}(r)\mathcal{O}(\infty)\right>_{\gamma}^{\mathrm{ext}}=|w'(r)|^{h}\left<\mathcal{O}(w(r))\mathcal{O}(\infty)\right>,
\end{equation}
where $h$ is conformal weight of $\mathcal{O}$. So
\begin{equation}
  \label{eq:155}
  \prec|w'(r)|^{h}\succ\sim\frac{ \left<\psi_{0,1}(0) \mathcal{O}(r)\Psi(\infty)\right>}{\left<\mathcal{O}(w(r))\mathcal{O}(\infty)\right>}
\end{equation}

To get Hausdorff dimension $d_{H}=1+\Delta(1)$ \eqref{eq:150} we need to insert operator
$V_{\alpha(1)/2,\alpha(1)/2}$, since we consider system with boundary. Then it fuses with its image
and produce vertex operator with conformal weight $h=1$. 
\begin{equation}
  \label{eq:156}
  \prec|w'(r)|^{2h(\alpha(1)/2)}\succ\sim\frac{\left< V_{\alpha(1)/2}(z) V_{\alpha(1)/2}(z^{*}) \psi_{0,1}(0) \Psi(\infty)\right>}{\left<V_{\alpha(1)/2}(w(z)) V_{\alpha(1)/2}(w^{*}(z))\right>}
\end{equation}

Use the formula \eqref{eq:157} to calculate correlation functions on the right-hand side. The
numerator gives us $r^{2\alpha_{0,1}\alpha(1)}$ for $z,z^{*}\to r,\; z-z^{*}\to 0$, the denominator
$(w(z)-w^{*}(z))^{\alpha(1)^{2}/2}\sim (|z| |w'(z)|)^{\alpha(1)^{2}/2}$. So total power of $|w'(r)|$
is 
$2h(\alpha(1)/2)+\alpha(1)^{2}/2=\alpha(1)
(\alpha(1)/2-2\alpha_{0})+\alpha(1)^{2}/2=\alpha(1)(\alpha(1)-2\alpha_{0})=1$, and total power of
$r$ is $2\alpha_{0,1}\alpha(1)-\alpha(1)^{2}/2$
\begin{equation}
  \label{eq:158}
  \prec |w'(r)|\succ \sim r^{\Delta(1)}=r^{2\alpha_{0,1}\alpha(1)-\alpha(1)^{2}/2}
\end{equation}

If we substitute $h_{0,1}=\frac{1}{2}-\frac{\kappa}{16}$ and
$2\alpha_{0}=\frac{\sqrt{\kappa}}{2}-\frac{2}{\sqrt{\kappa}}$ we obtain $\Delta(1)=\frac{\kappa}{8}$.

%%  To see it one can consider circle of small radius $\varepsilon$ centered at $z$. Put some conformal
%%  boundary condition on one half of the circle and another condition on the rest of the circle. Then
%%  critical curve would join the points of change in boundary conditions. The expectation values of
%%  observables in this geometry are given by CFT correlation functions with two boundary condition
%%  changing operators inserted:
%%  \begin{equation}
%%    \label{eq:119}
%%    \left< \Psi_{12}(z')\Psi_{12}(z'')\right>
%%  \end{equation}
%%  where $|z'-z|\leq \varepsilon$ and $|z''-z|\leq \varepsilon$. The boundary condition changing
%%  operators in Coulomb gas picture can be presented as the vertex operators
%%  $V_{\alpha_{12}}=e^{i\sqrt{2}\alpha_{12}\varphi(z)}$. When $\varepsilon\to 0$ we can fuse this two
%%  operators to single operator $V_{2\alpha_{12}}$. Note that $\alpha_{12}=-\frac{1}{2}\alpha_{-}$
%%  \eqref{eq:55}, so $V_{2\alpha_{12}}\sim V_{-\alpha_{-}}\sim V_{\alpha_{+}}$ (?)
%%  
%%  
%%  The moments of harmonic measure are connected with the CFT correlation functions by
%%  \begin{equation}
%%    \label{eq:118}
%%    \left<O_{h}(r) \Psi_{10}(0)\Psi(\infty)\right>\sim r^{h'-2h}\prec |w'(r)|^{h}\succ
%%  \end{equation}
%%  
%%  
%%  
%%  
%%
